Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-28 paper.tex
corrected comments 1

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}
\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
\newcommand{\tristan}[1]{\color{blue}From Tristan: #1\color{black}}

@@

No doubt containers have gained a lot of popularity, however containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns.
They also share three main security threats with other virtualization
techniques~\cite{gantikow2016providing}.

@@

However, two features of the Linux kernel,\textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Besides web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. This popularity of containers leads us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}.

To answer that question, we scan images that are used on Compute
Canada clusters by the Neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: Static scanning and Dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unauthorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that, containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also Singularity came up with Stools, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. The next section of this paper is about the results. Here, we
present a number of vulnerabilities that are present in the container images
which are used for data analysis on shared HPC clusters. Following section is about 
the discussion of these results where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
rules that can be followed to secure container images for use in clusters.

@@

This study involves four image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside the images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the second experiment of our study. The next 
experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.
Lastly, our fourth experiment involves both updating and shrinking the image size and then
rescanning for the vulnerabilities. \tristan{Content of this paragraph is fine, but writing is very convoluted.}

Here, we first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. 
Later, this section
presents two scanning techniques followed by a description of image scanners used.
In this study, we used three different image scanners because they
use different scanning techniques and/or refer to different vulnerability sources.
The images used in our study have different Linux distributions/releases, which have
different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

@@

We scanned a total of 44 container images taken from the BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
frameworks, two containerization frameworks used in neuroscience to share
and re-use applications. Among the 27 BIDS apps available at the time of
the study \tristan{mention link where the apps are listed}, we studied 26
unique Docker images as one wasn't available on DockerHub. Among the 49
Boutiques applications available at the time of the study, listed using
Boutiques \texttt{bosh search} command, 23 unique container images were
listed including 3 that couldn't be retrieved and 2 that were already
included in BIDS apps. The resulting 18 images included 12 Docker images
and 6 Singularity images.
\tristan{I rewrote this paragraph to focus it on the information of relevance for the reader. 
You could take it as an example for other sections of the paper.}

@@

We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{refneeded}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls is dynamic and the other
ones are static. To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
\begin{comment}
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
\begin{comment}
Anchore offers services in two ways: Anchore Engine and Anchore
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. 
\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.

In our experiments, we used Vuls Docker image having version v0.9.0 with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

@@

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after the update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random \tristan{Probably not really at random... 
No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}[t]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. At the time of writing, these reasons include bugs in scanners,
some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
and how frequently they are updating their databases, etc.

We have explained these differences below in detail
and have provided an example with each reason to make it clear.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

>>>>

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\change}[2]{\color{cyan}Changes: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}
\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
\newcommand{\tristan}[1]{\color{blue}From Tristan: #1\color{black}}

@@

No doubt containers have gained a lot of popularity, however containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns.
They also share three main security threats with other virtualization
techniques~\cite{gantikow2016providing}:

@@

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Besides web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. This popularity of containers leads us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}

To answer that question, we scan images that are used on Compute
Canada clusters by the Neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: Static scanning and Dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unauthorized actions on the target computer.
In this paper, we report vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. The next section of this paper provides the results, where we
present a number of existing vulnerabilities in the container images
used for data analysis on shared HPC clusters. We then proceed in the following section with 
discussion and analysis of these results, where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by proposing some
particular rules that can be followed to secure container images for use in clusters.

@@

\change{This study involves several image scanning experiments. To begin with,
we scan the images as is to report the existing vulnerabilities
inside the images. Updating these images is likely to play a role in vulnerabilities. Therefore, we
update the images and then rescan all these
images.
Subsequently, we shrink the size of the images
meaning that remove unnecessary packages from the images to see the effect on the number of
vulnerabilities in the images.
Lastly, we update and shrink the image size together and then
rescan for the vulnerabilities.

In this section, we first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we provide more insight
into the container images and the image scanners that we used in our study.
The image scanners are going to report different results due to different Linux
distributions/releases, which have different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.}

@@

We scanned a total of 44 container images taken from the BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
frameworks, two containerization frameworks used in neuroscience to share
and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
the study, we studied 26
unique Docker images as one wasn't available on DockerHub. Among the 49
Boutiques applications available at the time of the study, listed using
Boutiques \texttt{bosh search} command, 23 unique container images were
listed including 3 that couldn't be retrieved and 2 that were already
included in BIDS apps. The resulting 18 images included 12 Docker images
and 6 Singularity images.
\tristan{I rewrote this paragraph to focus it on the information of relevance for the reader. 
You could take it as an example for other sections of the paper.}

@@

We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls is a dynamic scanner, while the others
are static scanners. To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. Fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.

In our experiments, we used Vuls Docker image having version 0.9.0 with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

@@

Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution, we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for 
vulnerability data, it may lead to discrepancies in results.
Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

@@

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we use
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we get a list of packages from Reprozip that are needed for the application execution. 
After that, we expand this list by adding important and required packages that are essential
for the system to function and finally figure out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we keep these packages and remove remaining unnecessary packages. We use a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. We then discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities.
\tristan{Probably not really at random... 
No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

\begin{figure*}[t]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Numner of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. At the time of writing, these reasons include
some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
how frequently they are updating their databases, and bugs in scanners, etc.

We explain these differences below in detail
and provide an example with each reason to make it clear.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
